---
title: "Overview"
author: "Matthew Schuwminger"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  
  output:
  rmarkdown::html_vignette:
    fig_caption: yes
---

**mkedata** takes care of much of the grunt work of acquiring and 
processing Milwaukee data. This puts you much closer to doing what you most 
care about: ***analyzing and visualizing Milwaukee data***.

## Exploring Milwaukee Crime Data

What's the citywide trend in homicides?
```{r}
library(mkedata)
data("crimes.munged")
h <- subset(crimes.munged, OFFENSE1 == "HOMICIDE")
barplot(table(h$year))
```

## Mapping Milwaukee Data

Let's look at where those homicides took place in 2015. First overall, then in 
and around the Avenues West Business Improvement District.

```{r, fig.show='hold', fig.cap = "Your figure caption."}
library(sp)
mkeoutline <- to_nad27(mkeoutline)
h2015 <- subset(crimes.munged, OFFENSE1 == "HOMICIDE" & year == "2015")
plot(mkeoutline)
plot(h2015, col = "salmon", add = T)

bids <- to_nad27(bids)
plot(subset(bids, Name == "Avenues West"))
plot(h2015, col = "salmon", add = T)
```


Using **ggmap** and a transformation of the coordinates to the web map standard 
projection (WGS84), we can plot these crimes on a basemap for context:
```{r, message=FALSE, warning=TRUE}
library(ggmap)
h.wgs84 <- to_wgs84(h2015) 
m <- data.frame(slot(h.wgs84, "coords"), slot(h.wgs84, "data"))
    names(m)[1:2] <- c("lon", "lat")
    qmplot(lon, lat, data = m, color = I("salmon"))
```

